### 2014-04-29 Equipment/Equipment_Manual/Equipment_Manual.tex
Equipment Manual: Update to video editing section

\documentclass[12pt,oneside]{book}

@@

The GoPro cameras and DVR split long videos into multiple files. If you need to combine multiple .mp4 videos into one file, you can use a tool such as MP4Box or Avidemux. Multiple video files can also result from the DVR if a video channel loses signal temporarily. If this is the case, be sure to add blank video to pad any time that passed while the video channel signal was lost.

>>>>

\documentclass[11pt,oneside]{book}

@@

The GoPro cameras and DVR split long videos into multiple files because of the format of the file systems that they write to. If you need to combine multiple .mp4 videos into one file, you can use a tool such as MP4Box or Avidemux. Multiple video files can also result from the DVR if a video channel temporarily loses signal. If this is the case, be sure to add blank video to pad any time that passed while the video channel signal was lost.

For example, to seamlessly combine two video files (video\_1.mp4 and video\_2.mp4) into one video file (video\_output.mp4), the command line tool MP4Box can be used with the following command

\begin{verbatim}
MP4Box -cat video_1.mp4 -cat video_2.mp4 -new video_output.mp4
\end{verbatim}
